
\documentclass{article}
\usepackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}

\def\bbdot{\dot{\bb}}
\def\bgdot{\dot{\bg}}
\def\gdot{\dot{g}}
\def\ccdot{\dot{c}}
\def\adot{\dot{\ba}}
\def\bdot{\dot{\bb}}
\def\tdot{\dot{\bt}}
\def\tdd{\ddot{t}}
\def\addd{\ddot{a}}
\def\bdd{\ddot{b}}
\def\thetadot{\dot{\btheta}}
\def\covhat{\widehat{\cov}}
\def\sE{\mathbb{E}}
\def\bggt{\boldsymbol{\gamma\gamma'}}

\linespread{1.5}

\usepackage[margin=1in]{geometry}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\title{Some theoretical results}
\RequirePackage{amsthm,amsmath,geometry,amsfonts}
\RequirePackage[numbers]{natbib}
\usepackage[utf8]{inputenc}
\begin{document}

\section{Lunceford \& Davidian 2004 Stat. Med. \cite{Lunceford2004}}
\begin{itemize}
\item
Covariates are $(\mathbf{X, V}) = (X_1, X_2, X_3, V_1, V_2, V_3)$.  \\
$X_3 \sim Bernoulli(.2)$\\
$V_3 |X_3 \sim Bernoulli( .75X_3 +.25(1-X_3)$\\
\begin{displaymath}
\begin{pmatrix}X_1\\ V_1 \\X_2\\V_2  \end{pmatrix} | X_3 \sim 
N(\boldsymbol\mu_{X_3} , \begin{pmatrix}
	1 & .5 & -.5 & -.5\\
	   & 1 & -.5 & -.5 \\
	    &   & 1  & .5 \\
	    &  &   &  1
\end{pmatrix}),
\end{displaymath}
where $\mu_1 = (1, 1, -1, -1)', \mu_0 = (-1, -1, 1, 1)'$.
\item
PS:  $[ 1 + \exp( 0.6X_1 - 0.6X_2 + 0.6X_3)]^{-1}$
\item 
Misspecified PS:Leaving $X_1$ out
\item 
Outcome: $Y= -0.1X_1 + X_2 - X_3 + 2Z - V_1 + V_2 + V_3 + \epsilon$, where $Z$ is the treatment flag, $\epsilon \sim N(0,1)$
\item 
Misspecified outcome: Leaving $X_1, V_1$ out
\item True ATE: $v_4$ homogeneous
\item Misspecification type: omitted variable 
\end{itemize}

\section{Kang \& Schafer, 2007, Stat. Sci. \cite{Kang2007}}
\begin{itemize}
\item Covariates:  $z_1, \ldots z_4 \sim N(0,1)$ independently
\item PS: $expit(-z_1 + 0.5z_2 -0.25z_3 - 0.1z_4)$
\item 
Misspecified PS: Use $x_1, \ldots, x_4$ below as predictors 
\begin{displaymath} \begin{split} x_1 = exp(z_1/2)  \\
x_2 = z_2 /(1+exp(z_1)) + 10\\
x_3 = (z_1z_3/25 + .6)^3 \\
x_4 = (z_2 +z_4 +20)^2 
\end{split}\end{displaymath}
\item Outcome:  $y \sim N(\mu, 1)$, $\mu = 210 + 40d  + 27.4 z_1 + 13.7z_2 + 13.7z_3+ 13.7z_4$\\
\item Misspecified outcome: use $x_1, \ldots, x_4$ as predictors
\item True ATE:  40 homogeneous 
\item Misspecification type: nonlinearity
\end{itemize}


\section{Waernbaum 2012, Stat. Med. \cite{Waernbaum2012}}
\begin{itemize}
\item Covariates: $x_1, x_2 \sim Uniform(1, 5)$ independently
\item PS: $expit(0.36-1.25x_1-1.25x_2 + .36 x_1^2 + .35x_2^2)$
\item Misspecified PS: probit link 
\item Outcome: $y \sim Poisson(\mu)$, where $\mu = 2d + exp(1+.2x_1 + .2x_2)$ and $d$ marks treatment
\item Misspecified outcome: Identity link in place of Poisson regression.
\item True ATE: 2 homogeneous 
\item Misspecification type: nonlinearity
\end{itemize}


\section{Austin 2009 Biometrical J. \cite{Austin2009}}
\begin{itemize}
\item Covariates:\\
$C_1, \ldots, C_5 \sim N(0, 1)$ for the control group\\
$C_i, i=1,\ldots,5 \sim N(.2+.1(i-1), 1)$ for the treatment group\\
$B_i, i=1,\ldots,5 \sim Bernoulli(.1i)$ for the control group\\
$B_i, i=1,\ldots,5 \sim Bernoulli(\pi_i)$ for the treatment group\\
where $\pi_1 = 0.168, \pi_2 = 0.331, \pi_3 = 0.492, \pi_4 = 0.642, \pi_5 = 0.776$
All independent
\item PS:  20\% treated. True PS model should be a likelihood ratio from a mixture model {\color{red} I don't understand what you mean here - I just used all of the predictors.}.
\item Misspecified PS: Omit $C_3, B_3$. {\color{red}  I guess this isn's misspecified.}
\item Outcome: $Y=-2.8 +  1.5C_1 + 2C_2 +3C_3 +4C_4 +5B_1 +4B_2 + 3B_3 + 2B_4 +1.5B_5 + T + N(0, 4)$
\item Misspecified outcome: Omit $C_3, B_3$.
\item True ATE: 1 homogeneous 
\item Misspecification type: Omitting variables.
\end{itemize}

\section{Fan, Imai et al. 2016 \cite{Fan2016}}
\begin{itemize}
\item Covariates: $x_1, \ldots, x_4 \sim N(3, 2)$ independently {\color{red} I did $N(0, 1)$ - change?}
\item PS: $expit(- x_1 +.5x_2 -.25x_3 -.1x_4)$ 
\item Misspecified PS:  $x_1^* = exp(x_1/3), x_2^*=x_2/(1+exp(x_1))+10, x_3^*=x_1x_3/25 + .6, x_4^* = {\color{red} x_2} +x_4 + 20$.  True PS generated from the star version, but original predictors used in modeling
\item Outcome: $y = 200 + 27.4 x_1d + 13.7 x_2 + 13.7x_4 + N(0,1)$.
\item Misspecified outcome: True outcome changes to 
$Y = 200 + 27.4x_1^2d + 13.7x_2^2 + 13.7x_3^2+ 13.7x_4^2$ but linear model fit.
\item True ATE: 0
\item Misspecification type:  nonlinearity
\end{itemize}

\section{Iacus, King, Porro, 2012 Political Analysis \cite{Iacus2009}}
{\color{red} The paper Denis sent was Iacus et al, 2009 J. Stat. Soft., which lacked DGP details}
\begin{itemize}
\item Covariates: empirical data re74, re75, education, age, educ, black, Hispanic, married, nodegree, u74 u75.  Except for earnings (re74, re75), others are either categorical or dichotomous. 
\item PS: $expit(1+.5\hat \mu + .01age^2 -.3 education^2 - .01\log(re74+.01)^2 + .01\log(re75+.01)^2)$ where \\
$\hat\mu = 1+1.428e-4 age^2 -2.918e-3 educ^2 - .2275black - .8276 hispanic + .2071 married - .8232 nodegree -1.236e-9 re74^2 + 5.868e-10 re75^2 - .04328 u74 - .3804 u75$
\item Misspecified PS: Covariate: Age, educ, black, hisp, married, hodegr, u74, u75, re74, re75. 
\item Outcome: $Y = 1000T + .1\exp(.7*\log(re74+.01 + .7log(re75+.01)) + N(0, 10)$
\item Misspecified outcome: "Correct" outcome model an interaction of spline terms for re74 and re75 (maybe this is bad?). Misspecified outcome is same as misspecified PS.
\item True ATE: 1000 homogenous
\item Misspecification type: nonlinearity
\end{itemize}

\section{Leacy and Stuart, 2014 Stat. Med. \cite{Leacy2014}}
\begin{itemize}
\item Covariates: $W_1, \ldots, W_{10} \sim N(0,\Sigma)$, $\Sigma_{15} = \Sigma_{51} = \Sigma_{38} = \Sigma_{83} = 0.2, \Sigma_{26} = \Sigma_{62} = \Sigma_{39} = \Sigma_{93} = 0.9$  \\  $W_1, W_3, W_5, W_6, W_8, W_9$ dichotomized at 0
\item PS: \begin{align*}
\text{expit}\{&-1.897 + 0.8W_1 + -0.25W_2 + 0.6W_3 + -0.4W_4 + -0.8W_5 + -0.5W_6 + 0.7W_7 +\\
              &\quad-0.25W_2^2 + -0.4W_4^2 + 0.7W_7^2 + 0.5 \times0.8W_1W_3 +\\
               &\quad0.7 \times(-0.25)W_2W_4 + 0.5 \times0.6W_3W_5 + 0.7 \times(-0.4)W_6W_4 +\\
               &\quad0.5 \times(-0.8)W_5W_7 + 0.5 \times0.8W_1W_6 + 0.7 \times(-0.25)W_2W_3 +\\
               &\quad0.5 \times0.6W_3W_4 + 0.5 \times(-0.4)W_5W_4 + 0.5 \times(-0.8)W_5W_6\}
               \end{align*}
\item Misspecified PS: Linear in $W_1, ..., W_{10}$
\item Outcome: 
\begin{align*}
Y &= -1.386 - 0.4*D + 0.3W_1 + -0.36W_2 + -0.73W_3 + -0.2W_4 + 0.71W_8 + -0.19W_9 + 0.26W_10 +\\
              &\quad-0.36W_2^2 + -0.2W_4^2 + 0.26W_{10}^2 + 0.5 \times0.3W_1W_3 +\\
               &\quad0.7 \times(-0.36)W_2W_4 + 0.5 \times(-0.73)W_3W_8 + 0.7 \times(-0.2)W_9W_4 +\\
               &\quad0.5 \times(0.71)W_8W_{10} + 0.5 \times0.3W_1W_9 + 0.7 \times(-0.36)W_2W_3 +\\
               &\quad0.5 \times(-0.73)W_3W_4 + 0.5 \times(-0.2)W_8W_4 + 0.5 \times(0.71)W_8W_9 + \epsilon
\end{align*}
\item Misspecified Outcome: Linear in $W_1, ..., W_{10}$
\item True ATE: -0.4 homogenous
\item Misspecification type: nonlinearity
\end{itemize}

\bibliography{refs.bib}
\bibliographystyle{plain}

\end{document}
