---
output:
  md_document:
    variant: markdown_github
bibliography: refs.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  warning = FALSE, 
  message = FALSE,
  collapse = TRUE,
  cache = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# synthate package: Synthetic estimators for the average treatment effect

This package comprises a suite of tools to simulate various data-generating processes. Its purpose is to check the operating characteristics of various causal estimators and to optimally combine them.

## Installation

The `synthate` package can currently be obtained from GitLab: https://code.rand.org/agniel-projects/personal-packages/synthate or from GitHub at https://github.com/denisagniel/synthate. It may be downloaded by running

```{r eval=FALSE}
devtools::install_github('denisagniel/synthate')
```

## Overview

There are three main features of `synthate`:

- Simulating data
- Causal estimation
- Combining estimators

### Simulating data

There are currently seven DGPs derived from six different papers to choose from:

Short-hand        | Paper
---------------------|---------------------------------
`ks`             | Kang and Schafer (@Kang2007)
`ld`             | Lunceford and Davidian (@Lunceford2004)
`iw`             | Waernbaum (@Waernbaum2012)
`fi`         | Fan and Imai (@Fan2016)
`pa`           | Austin (@Austin2009)
`ls`             | Leacy and Stuart (@Leacy2014)
`ik`             | Iacus and King (@Iacus2009)

## References
